Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-22 paper/supplemental/architecture.tex
Minor changes

\subsection{Architecture}
We explored different architectures for the convolutional neural network (CNN) for split error detection. In table \ref{tab:architecture} we compare traditional CNN architectures versus residual networks~\cite{resnet}. The traditional architecture with dropout regularization generalized better than residual networks on unseen testing data.

\begin{table}[h]
\caption{Traditional CNN Architecture versus Residual Network Architecture \cite{resnet}. All configurations are compared using the same parameters. Our final choice (indicated by *) trains relatively fast and performs better.}%While the training of our classifier is more expensive, testing accuracy is superior. }

@@

We performed a limited brute force parameter search to tune the split error classifier (Tab. \ref{tab:parametersearch}). This resulted in 3240 different CNN configurations which were evaluated on 10\% of our training data. Learning rate and momentum ranges are defined linearly across 2000 epochs.

\begin{table}[h]
\caption{Brute force parameter search for the split error classifier. The final parameters are highlighted.}%While the training of our classifier is more expensive, testing accuracy is superior. }

@@

\subsection{Automatic Method Threshold $p_t$}
For automatic selection, we observed a threshold $p_t=0.95$ as stable when evaluating on previously unseen testing data (Mouse S1 AC3 Open Connectome Project dataset). This means, that automatic selection stops once all borders with $p_t\geq0.95$ were proofread. Fig. \ref{fig:pt} shows split error classification on three randomly selected subvolumes ($700\times700\times2$ voxels) of AC3. In all cases, the threshold $p_t=0.95$ reduces VI.

>>>>

\subsection{Architecture}
We explored different architectures for the convolutional neural network (CNN) for split error detection. We compare traditional CNN architectures versus residual networks~\cite{resnet} (Tab.~\ref{tab:architecture}). The traditional architecture with dropout regularization generalized better than residual networks on unseen testing data.

\begin{table}[t]
\caption{Traditional CNN Architecture versus Residual Network Architecture \cite{resnet}. All configurations are compared using the same parameters. Our final choice (indicated by *) trains relatively fast and performs better.}%While the training of our classifier is more expensive, testing accuracy is superior. }

@@

We performed a limited brute force parameter search to tune the split error classifier (Tab.~\ref{tab:parametersearch}). This resulted in 3240 different CNN configurations which were evaluated on 10\% of our training data. Learning rate and momentum ranges are defined linearly across 2000 epochs.

\begin{table}[t]
\caption{Brute force parameter search for the split error classifier. The final parameters are highlighted.}%While the training of our classifier is more expensive, testing accuracy is superior. }

@@

\subsection{Automatic Method Threshold $p_t$}
For automatic selection, we observed a threshold $p_t=0.95$ as stable when evaluating on previously unseen testing data (Mouse S1 AC3 Open Connectome Project dataset). This means that automatic selection stops once all borders with $p_t\geq0.95$ were proofread. Figure~\ref{fig:cylboxplot} shows split error classification on three randomly selected subvolumes ($700\times700\times2$ voxels) of AC3. In all cases, the threshold $p_t=0.95$ reduces VI.
